Appendix A

### 2020-10-05 appendixA/appendixA.Rmd
finished appendix and saving parameter outputs for simulations

################# COPY PASTE OF INDIVIDUAL

@@

```{r}
# Create the dataframe that compares the models by information criteria
nice_fams_prms %>% 
  filter(., data != "POP") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "Exponential", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "Family") %>% 
  full_join(., nice_prms %>%
              filter(., data == "POP") %>% 
              dplyr::select(dist, BIC, AIC, AICc, deltaAIC, deltaAICc, deltaBIC) %>% 
              distinct() %>% 
              mutate(data = "Population")) -> popfam.IC.comp

@@

####################################################################################

```{r}
all_fam_prms <- prms.fams.df %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3))
```

```{r}
prms.fams.df %>% 
  mutate(fit.param = paste(dist, param)) %>% 
  ggplot(., aes(x = data, y = estimate, color = dist)) +
  facet_wrap(~fit.param, scales = "free") +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
  theme(legend.position = "none")
```

## Calculate BIC for comparisons

```{r fig.height=6}
prms.fams.df %>% 
  dplyr::select(., loglik, n, dist, data) %>% 
  distinct() %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.IC

popfam.IC %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")

Calculate BIC for the model at the family level
```{r}
prms.fams.df %>% 
  filter(., data != "pop") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "fam") %>% 
  full_join(., popfam.IC %>% 
  filter(., data == "pop")) -> comp.fams

comp.fams %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")

comp.fams %>% 
  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = dist, y = value, color = data)) +
  geom_point() +
  facet_wrap(~ic, scales = "free")

```
```{r}

# Get the multi-distribution model fit
popfam.IC %>% 
  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
  ungroup() %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  as.numeric() -> multi.BIC

popfam.IC %>% 
  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
  ungroup() %>% 
  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
  as.numeric() -> multi.AIC

popfam.IC %>% 
  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
  ungroup() %>% 
  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
  as.numeric()-> multi.AICc

comp.fams %>% 
  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
  bind_rows(., data.frame(dist = "multi", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "multi")) %>% 
  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = dist, y = value, color = data)) +
  geom_point() +
  facet_wrap(~ic, scales = "free") +
  theme(axis.text.x = element_text(angle = 90))

@@

```{r eval = FALSE}
# Save parameters

saveRDS(all_indiv_prms, file = "appendixA/popindprms.RDS")
saveRDS(all_fam_prms, file = "appendixA/popfamprms.RDS")

>>>>

@@

```{r}
# Create the dataframe that compares the models by information criteria
nice_fams_prms %>% 
  filter(., data != "POP") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "Exponential", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "Family") %>% 
  full_join(., nice_fams_prms %>%
              filter(., data == "POP") %>% 
              dplyr::select(dist, BIC, AIC, AICc, deltaAIC, deltaAICc, deltaBIC) %>% 
              distinct() %>% 
              mutate(data = "Population")) -> popfam.IC.comp

@@

@@

```{r}
# Save parameters

saveRDS(nice_prms, file = "appendixA/popindprms.RDS")
saveRDS(nice_fams_prms, file = "appendixA/popfamprms.RDS")
